Machine learning topological phases in real space

### 2020-07-28 10_prb_resubmission_01/letter_referee/letter_referee.tex
Submitted to Arxiv and PRB

we appreciate the time spent by you and both referees in reviewing our manuscript \emph{Machine learning topological phases in real space} (BS13900). We have fully addressed the issues pointed by referee 2, which have led to a much improved version of the paper, hopefully the definitive version.

In what follows, we briefly summarize the modifications made to the paper. New results have been added to the paper in the form of two new sections: \textbf{V. Topological feature engineering and lattice compression} and \textbf{VI. Emergent information entropy wave functions}. We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II. The eigenvector ensembling algorithm}. The section \textbf{VII. Discussion} has been extended to address the issues that were raised. The sections are now numbered for clarity.

@@

we appreciate the time spent by you in reviewing our manuscript \emph{Machine learning topological phases in real space}. We are currently cleaning, pruning and documenting our code, so we expect to put the Python code used to run the numerical experiments described in the paper online as soon as possible.

@@

we appreciate the valuable insights on how to improve our article \emph{Machine learning topological phases in real space} that you have provided us with. These insights forced us into more careful theoretical reasoning about the results we had obtained and led us to expand our manuscript with new theoretical and numerical contents.

A summary of the modifications made to the paper are listed in what follows. New results have been added to the paper in the form of two new sections: \textbf{V. Topological feature engineering and lattice compression} and \textbf{VI. Emergent information entropy wave functions}. We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II. The eigenvector ensembling algorithm}. The section \textbf{VII. Discussion} has been extended to include comments on the issues that were raised. The sections are now numbered for clarity.

>>>>

We appreciate the time spent by you and both referees in reviewing our manuscript \emph{Machine learning topological phases in real space} (BS13900). We have fully addressed the issues pointed by referee 2, which have led to a much improved version of the paper, hopefully the definitive version.

In what follows, we briefly summarize the modifications made to the paper. New results have been added to the paper in the form of two new sections: \textbf{V. Topological feature engineering and lattice compression} and \textbf{VI. Emergent information entropy wave functions}. We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II. The eigenvector ensembling algorithm}. The sections \textbf{I. Introduction}, \textbf{VII. Discussion} as well as the \textbf{Abstract} have been extended to conform with these additions. The sections are now numbered for clarity.

@@

We appreciate the time spent by you in reviewing our manuscript \emph{Machine learning topological phases in real space}. We are currently cleaning, pruning and documenting our code, so we expect to put the Python code used to run the numerical experiments described in the paper online as soon as possible.

@@

We appreciate the valuable insights on how to improve our article \emph{Machine learning topological phases in real space} that you have provided us with. These insights forced us into more careful theoretical reasoning about the results we had obtained and led us to expand our manuscript with new theoretical and numerical contents.

A summary of the modifications made to the paper are listed in what follows. New results have been added to the paper in the form of two new sections: \textbf{V. Topological feature engineering and lattice compression} and \textbf{VI. Emergent information entropy wave functions}. We have also moved the description of the eigenvector ensembling algorithm from the \textbf{Supplementary material} to the main text, in which it became the section \textbf{II. The eigenvector ensembling algorithm}. The sections \textbf{I. Introduction}, \textbf{VII. Discussion} as well as the \textbf{Abstract} have been extended to conform with these additions. The sections are now numbered for clarity.
